### 2017-12-06 submission/manuscript.Rmd
add general analysis workflow to methods

>>>>

***Analysis Workflow:***
The total number of OTUs after sub-sampling was analyzed for both the fecal and mock community samples. From these observations we wanted to next analyze potential reasons as to why some of these differences may have occured. First, analysis of general sequence error rate, number of sequences with an error, and base subsitution were assessed in the mock community for each Taq. After assessing these errors, the total number of chimeras was determined after sequence processing. The fecal samples were analyzed at 4 different sub-sampling levels, 1000, 5000, 10000, and 15000 while the mock community samples were analysed at 3 levels, 1000, 5000, 10000.

### 2017-12-06 submission/manuscript.tex
add general analysis workflow to methods

>>>>

\textbf{\emph{Analysis Workflow:}} The total number of OTUs after
sub-sampling was analyzed for both the fecal and mock community samples.
From these observations we wanted to next analyze potential reasons as
to why some of these differences may have occured. First, analysis of
general sequence error rate, number of sequences with an error, and base
subsitution were assessed in the mock community for each Taq. After
assessing these errors, the total number of chimeras was determined
after sequence processing. The fecal samples were analyzed at 4
different sub-sampling levels, 1000, 5000, 10000, and 15000 while the
mock community samples were analysed at 3 levels, 1000, 5000, 10000.
